---
title: "Dev pilot network"
author: "Pitchayen S."
date: "12/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setlocale(locale = "Thai")
```

## Prerequisite

```{r}
library(tidyverse)

source("conn.R")
source("utility.R")
```

```{r}
spec_filter <- "Otorhinolaryngology"
```


## Data Preparation

### Extraction

```{r}
event <- tbl(con, sql("SELECT * FROM cim_cdm_pub.vw_f_event"))

event %>% 
  filter(evnt_type %in% c("Small Meeting with External Speaker", 
                          "Sales Initiated Lecture/Symposium"), 
         evnt_end_date >= as.Date("2019-01-01"), 
         evnt_end_date <= as.Date("2021-12-31"), 
         dm_deleted_flag == "N",
         dm_current_flag == "Y",) -> event_select

event_speaker <- tbl(con, sql("SELECT * FROM cim_cdm_pub.vw_f_event_speaker"))

speaker_profile <- tbl(con, sql("SELECT * FROM cim_cdm_pub.vw_d_speaker"))

speaker_qual <- tbl(con, sql("SELECT * FROM cim_cdm_pub.vw_d_speaker_qualification"))

event_attendee <- tbl(con, sql("SELECT * FROM cim_cdm_pub.vw_f_event_attendee"))
```

Loading customer data

```{r}
cust <- tbl(con, sql("SELECT * FROM cim_cdm_pub.vw_d_customer"))

cust %>% 
  filter(cust_status_code_local == "Active", 
         cust_class_of_trade == "Physician", 
         dm_deleted_flag == "N", 
         dm_current_flag == "Y") -> cust

cust_child <- tbl(con, sql("SELECT * FROM cim_lc_pub.vw_c302_009_child_account"))

cust_child %>% 
  filter(da_deleted_flag == "N") -> cust_child
```

Selecting relevance data

```{r}
event_select %>%  
  filter(evnt_status == "Closed", is.na(parent_evnt_id)) %>% 
  select(evnt_key, evnt_id, evnt_id, parent_evnt_id, 
                      evnt_name, evnt_type, evnt_subtype) -> event_select

event_speaker %>% select(evnt_key, spk_key) -> event_speaker

speaker_profile %>% select(spk_key, cust_ak) %>%
  rename(cust_ak_speaker = cust_ak) -> speaker_profile

speaker_qual %>% select(spk_key, qualf_name) -> speaker_qual

event_attendee %>% 
  select(cust_ak, evnt_key) %>% 
  filter(!is.na(cust_ak)) -> event_attendee
```

```{r}
cust %>%
  select(cust_ak, cust_id ,cust_name, cust_veeva_id, cust_main_specialty_code, 
         cust_prmry_addr_state, cust_prmry_parent_name) -> cust

cust_child %>% 
  select(child_account_vod, parent_account_vod, primary_vod) -> cust_child
```

### Event data

#### Joining

Joining data

```{r}
event_select %>% 
  left_join(event_speaker, by ="evnt_key") %>% 
  left_join(speaker_profile, by ="spk_key") %>%
  left_join(speaker_qual, by ="spk_key") %>% 
  filter(!is.na(spk_key)) %>% 
  left_join(cust, by = c("cust_ak_speaker"="cust_ak"), suffix = c("", "_speaker")) %>%
  left_join(event_attendee, by = "evnt_key") %>%
  left_join(cust, by = "cust_ak", suffix = c("", "_attendee")) %>% 
  arrange(evnt_key) %>% 
  filter(!is.na(cust_id),
         cust_main_specialty_code_attendee != "Nurse") -> event_select

glimpse(event_select)
```

```{r}
event_select %>% 
  select(!c(evnt_key:evnt_name, evnt_subtype, spk_key, cust_veeva_id, cust_ak, cust_name_attendee,
           cust_veeva_id_attendee:cust_prmry_parent_name_attendee)) -> event_select

glimpse(event_select)
```

#### Transforming

Filtering for pilot

```{r}
event_select %>% 
  filter(evnt_type == "Small Meeting with External Speaker", 
         cust_main_specialty_code == spec_filter, 
         !is.na(cust_id_attendee)) -> small_mtg_joined
```

Creating event edge list

```{r}
small_mtg_joined %>% 
  filter(!is.na(cust_id_attendee)) %>% 
  select(from = cust_id_attendee, to = cust_id) %>% 
  mutate(init_weight = 10) %>% 
  group_by(from, to) %>% 
  summarise(weight = sum(init_weight)) %>% 
  collect() -> event_edge_list
```

Creating speaker profile table

```{r}
event_select %>%
  filter(cust_main_specialty_code == spec_filter) %>% 
  select(cust_id, cust_name, qualf_name, cust_main_specialty_code, cust_prmry_addr_state, cust_prmry_parent_name) %>% 
  distinct() %>% 
  collect() -> speaker_prof_tbl 
```


### HCO correlation

#### Joining child hco

```{r}
cust %>% 
  filter(cust_main_specialty_code == spec_filter) -> cust_filter

cust_filter %>% 
  inner_join(cust_child, by = c("cust_veeva_id"="child_account_vod")) %>% 
  arrange(cust_id) -> cust_filter

glimpse(cust_filter)
```

#### Joining relationship

```{r}
cust_filter %>% 
  select(cust_id, cust_main_specialty_code, parent_account_vod, primary_vod) %>% 
  rename(cust_id_to = cust_id) -> hcp_to

cust_filter %>% 
  select(cust_id, cust_main_specialty_code, parent_account_vod) %>% 
  rename(cust_id_from = cust_id) -> hcp_from
```

```{r}
hcp_from %>% 
  left_join(hcp_to, by = c("cust_main_specialty_code", "parent_account_vod")) %>% 
  filter(cust_id_from != cust_id_to) -> hcp_network
```

#### Transformation

```{r}
hcp_network %>% 
  mutate(init_weight = ifelse(primary_vod == "Yes", 3, 1)) %>% 
  select(from = cust_id_from, to = cust_id_to, init_weight) %>% 
  group_by(from, to) %>% 
  summarise(weight = sum(init_weight)) %>% 
  collect() -> hcp_edge
```
### Combined data

#### Edge list

```{r}
edge_list <- bind_rows(event_edge_list ,hcp_edge)

edge_list %>% 
  group_by(from, to) %>% 
  summarise(weight = sum(weight)) -> edge_list
```
### Node list

```{r}
cust %>%
  filter(cust_main_specialty_code == spec_filter) %>% 
  select(!c(cust_ak, cust_veeva_id)) %>%
  rename(id = cust_id, label = cust_name, title = cust_prmry_parent_name) %>% 
  collect() -> node_list
```

Mapping with speaker list

```{r}
speaker_prof_tbl %>% 
  select(id = cust_id) %>% 
  mutate(group = "Speaker") -> spk_flag

node_list %>% 
  left_join(spk_flag, by = "id") %>% 
  mutate(group = ifelse(is.na(group),"None", group)) -> node_list
```

### Filtering invalid hcp

```{r}
edge_list %>% 
  semi_join(node_list, by = c("from"="id")) %>% 
  semi_join(node_list, by = c("to"="id")) -> edge_list
```


## Graph

```{r}
library(tidygraph)
library(visNetwork)
```

### Converting into tidygraph object

```{r}
route_hcp <- tbl_graph(nodes = node_list, edges = edge_list,
                       node_key = "id",
                       directed = T)

route_hcp %>% 
  activate(nodes) %>% 
  mutate(eigen = round(centrality_eigen() * 100, digits = 2), 
         degree = centrality_degree(), 
         betweeness = centrality_betweenness()) -> route_hcp
```

Mapping the speaker profile

```{r}
route_hcp %>% 
  activate(nodes) %>% 
  as_tibble() %>% 
  filter(group == "Speaker") %>% 
  select(cust_id = id, eigen:betweeness) -> score_mapping

speaker_prof_tbl %>% 
  left_join(score_mapping, by = "cust_id") -> speaker_prof_tbl

speaker_prof_tbl

write_csv(speaker_prof_tbl, "output/speaker_prof_tbl.csv")

saveRDS(route_hcp, "output/hcp_graph_obj.RDS")
```

Writing Node list without speaker

```{r}
route_hcp %>% 
  activate(nodes) %>% 
  as_tibble() %>% 
  filter(group == "None") %>%
  write_csv("output/node_non_speaker.csv")
```


### Plotting the distribution

```{r}
route_hcp %>% 
  activate(nodes) %>% 
  as_tibble() %>% 
  ggplot(aes(x = eigen)) + geom_histogram()
```

```{r}
route_hcp %>% 
  activate(nodes) %>% 
  as_tibble() %>% 
  ggplot(aes(x = degree)) + geom_histogram()
```

```{r}
route_hcp %>% 
  activate(nodes) %>% 
  as_tibble() %>% 
  ggplot(aes(x = betweeness)) + geom_histogram()
```


### Graph plotting

```{r}
vis_tidy_graph_filter(route_hcp, eigen, 100)
```

```{r}
vis_tidy_graph_filter(route_hcp, betweeness, 100)
```

```{r}
vis_tidy_graph_filter(route_hcp, degree, 100)
```

## Closing redshift connection

```{r}
DBI::dbDisconnect(con)

```